---
title: "Es_207_hw2"
author: "Naivy Rodal"
date: "30/1/2020"
output: html_document
output: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#######################################################
# Example R Markdown Script                           #
# Adapted from:                                       #
# Tidy data and efficient manipulation              #
# Coding Club tutorial                              #  
# January 18th 2017                                 #
# Sandra Angers-Blondin (s.angers-blondin@ed.ac.uk) #
# John Godlee                                         #
# 24/Jan/2017                                         #
#######################################################

##The first thing to do is instal the packages so I can use the functions
#install.packages("pander")
#install.packages("tidyr")
#install.packages("dplyr")

##Then, you need to name the library to start using them
```{r}
library(dplyr) #  data manipulation package
library(tidyr) # a package to format your data
library(pander) #to create pretty tables
```
```{r, warning = FALSE}
library(dplyr)
##Open the file where I download the data set I am going to using 'setwd()'
##Import the data
```

```{r}
elongation <- read.csv("EmpetrumElongation.csv", sep = ";")
```

```{r, eval=FALSE}
germination <- read.csv("Germination.csv", sep = ";") #As elongation data does not exist I have to write the funtion nest to '{r}'
```

# Tidying the data
#Putting the data into long format using gather()
```{r, eval=FALSE}

elongation_long <- gather(elongation, Year, Length, c(X2007, X2008, X2009, X2010, X2011, X2012)) 
head("elongation_long")

```
```{r, eval=FALSE}
# Create a boxplot of `elongation_long' to visualise elongation for each year.
boxplot(Length ~ Year, 
        data = elongation_long, 
        xlab = "Year", 
        ylab = "Elongation (cm)", 
        main = "Annual growth of Empetrum hermaphroditum")
```

```{r, eval=FALSE}
# Filter() to keep only the rows of `germination' for species `SR' 
germinSR <- filter(germination, Species == 'SR')
```

```{r, eval=FALSE}
hist(germinSR$Nb_seeds_germin, breaks = 8)
##Creating a Histogram
# Mutate() is used to create a new column 
germin_percent <- mutate(germination, Percent = Nb_seeds_germin / Nb_seeds_tot * 100)
germin_summ <- germin_percent %>%
  group_by(Species) %>%
  summarise("Mean germination per" = mean(Nb_seeds_germin), "Max germination per" = max(Nb_seeds_germin), "Min germination per" = min(Nb_seeds_germin))
##Making a table
library(pander)
norm<- germin_summ(100, mean=0, sd=1)
germin_summ <- germin_percent %>%
  group_by(Species) %>%
  summarise("Mean germination per" = mean(Nb_seeds_germin), "Max germination per" = max(Nb_seeds_germin), "Min germination per" = min(Nb_seeds_germin))

## I can do this part because I do not have the file
```

```{r}
A<- c("a","a","b", "b")
B<- c(5, 10, 15, 20)
dataframe<- data.frame(A,B)
plot(dataframe)
##For this part I use the data in "Getting started with R Markdown"
```


```{r, include= FALSE}
library(pander)
plant<- c("a", "b")
temperature<- c(20,20)
growth<- c(0.65, 0.95)
dataframe<- data.frame(plant, temperature, growth)
emphasize.italics.cols(2)
pander(dataframe)
```
|Plant| Temp | Growth |
|:----|:-----|-------:|
|A    | 20   | 0.65   |
|B    | 20   | 0.95   |

```{r, echo=FALSE} 
library(broom)
A<- c(20, 15, 10)
B<- c(1,2,3)
lm_test <- lm(A~B)
summary(lm_test)
table_obj<- tidy(lm_test)
pander(table_obj,digits=3)
```




